Response to referee

### 2024-04-30 paper/article_jos.tex
v1

\usepackage{stmaryrd}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{animate, dsfont, here, xspace}
%\usepackage{tikz}
\usepackage{tikz,pgfplots}
 \pgfplotsset{compat=1.17}
%\includepdf[fitpaper=true, pages=-]{img/pdg.pdf}

@@

%\DefineBibliographyStrings{english}{andothers={et\addabbrvspace alii}}
\usepackage[authordate16,backend=biber,maxcitenames=2]{biblatex-chicago}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{biblatex}
\addbibresource{biblio.bib}
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Improving real-time trend estimates using local parametrisation of polynomial regression filters},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

This paper studies and compares real-time estimates of the trend-cycle
component with moving averages based on local polynomial regression. In
particular, this theory allows us to reproduce Henderson's symmetric and
Musgrave's asymmetric filters used in the X-13ARIMA-SEATS seasonal
adjustment algorithm. This paper proposes two extensions of local
polynomial filters for real-time trend-cycle estimates (for the last
estimates): first including a timeliness criterion to minimise the phase
shift; second, with procedure for parametrising asymmetric filters
locally While they are generally parametrised globally, which can be
suboptimal around turning points. An empirical comparison, based on
simulated and real data, shows that modelling polynomial trends that are
too complex introduces more revisions without reducing the phase shift,
and that local parametrisation reduces the delay in detecting turning
points and reduces revisions. The paper also shows how these results can
be easily reproduced using the R package \texttt{rjd3filters} dedicated
to the manipulation of moving averages.

@@

Analysis of the economic cycle, and in particular the early detection of
turning points in a series, is a major topic in the analysis of economic
outlook. To this end, economic indicators are generally seasonally
adjusted. However, in order to improve their interpretability, it may be
necessary to perform additional smoothing in order to reduce noise, and
thus analyse the trend-cycle component. By construction, trend-cycle
extraction methods are closely related to seasonal adjustment methods,
since they are generally applied to seasonally adjusted series.

A moving average, or linear filter, is a statistical method that
consists of applying a rolling weighted mean to a times series: for each
date \(t\) it computes a weighted mean of \(p\) past points and \(q\)
future points where \(p,q\geq0\) depends on the moving average. Moving
averages are ubiquitous in business cycle extraction and seasonal
adjustment methods. For example, the X-11 decomposition method
\autocite{x11}, used in X-13ARIMA-SEATS software \autocite{x13}, uses
several moving averages to estimate the main components of a time
series. Symmetric filters are applied to the center of the series, but
when it comes to estimate the most recent points, all of these methods
must rely on asymmetric filters. For trend-cycle extraction, the most
popular symmetric filter is the \textcite{henderson1916note} moving
average, which is used in the X-11 seasonal adjustment algorithm.

However, for real-time estimates, due to the lack of future
observations, all these methods must rely on asymmetric filters to
estimate the most recent points. For example, for trend-cycle
extraction, X-11 uses Henderson's symmetric filter and
\textcite{musgrave1964set}'s asymmetric filters on an extended series
using an ARIMA model. Since the predicted values are linear combinations
of past values, this amounts to applying asymmetric averages at the end
of the series.

If the classic asymmetric moving averages have good properties regarding
the future revisions induced by the process (see for example
\textcite{pierce1980SA}), they create, by construction, phase shifts
that impact the real-time estimation of turning points, introducing time
delay in the detection.

Using local polynomial regression, \textcite{proietti2008} developed a
general class of symmetric and asymmetric moving averages. In
particular, it becomes possible to reproduce Henderson's symmetric
filter and Musgrave's asymmetric filters. The aim of this study is to
propose two extensions to the \textcite{proietti2008} class of filters
in order to two drawbacks of those methods. Firstly, adding, in the
optimisation process, a timeliness criterin to directly control the
phase shift (i.e.~the delay in detecting turning points). Secondly,
calibrating asymmetric filter locally, while they are generally
calibrated globally using thus assumptions that may be wrong locally.
Those extensions are implemented in the statistical software R
\autocite{logicielr} throw the \texttt{rjd3filters} package (available
at \url{https://github.com/rjdemetra/rjd3filters}) and can therefore be
easily used. All the code associated to this paper is available at
\url{https://github.com/XXXX} (anonymized linked before the manuscript
is accepted).

@@

The basic assumption used in time series decomposition methods is that
the input observed time series, \(y_t\) can be decomposed into a signal
component \(\mu_t\) and a an erratic component \(\varepsilon_t\) (called
irregular): \[
f(y_t)=\mu_t+\varepsilon_t
\] where \(f\) denotes some appropriate transformation (usually
logarithmic or no transformation). To simplify further notations,
\(y_t\) will denote the transformed observed series. The noise component
\(\varepsilon_t\) is usually assumed to be a white noise. Assuming that
the input time series is seasonally adjusted (or without seasonality),
the signal \(\mu_t\) represents the trend and cycle components, here
estimated jointly and called trend-cycle \(TC_t\). This component can be
locally approximated by a polynomial degree (see
section~\ref{sec-nonparamreg}): \[
\mu_t = \sum_{j=0}^d\beta_jt^j+\xi_t
\] with \(\xi_t\) a stochastic process uncorrelated with
\(\varepsilon_t\). Even if some papers model \(\xi_t\) and
\(\varepsilon_t\) separately \autocite[see for
example][]{GrayThomson2002}, an usual assumption, adopted in this paper,
is to is to gather \(\xi_t\) and \(\varepsilon_t\). Thus, the
trend-cycle \(TC_t\) is considered as deterministic and modelled as a
polynomial trend of degree \(d\). The coefficients
\((\beta_0,\dots,\beta_k)\) can be estimated by weighted least squares.
The estimate \(\hat \beta_0\) provides the trend-cycle estimate
\(\hat TC_t\) and it can be shown that this equivalent to apply of
moving average (see section~\ref{sec-nonparamreg}). The goal of this
paper is to present two new methods to separate the trend-cycle
component from the noise component in real-time (i.e.~when no future
point is known), using moving averages build on local polynomial
smoothing techniques.

@@

Let \(p\) and \(f\) two integers, a moving average
\(M_{\boldsymbol\theta}\) or \(M\) is defined by a set of coefficients
\(\boldsymbol\theta=\transp{\begin{pmatrix}\theta_{-p}&\cdots&\theta_{f}\end{pmatrix}}\)
such as for all time series \(y_t\): \[
M_{\boldsymbol\theta}(y_t)=\sum_{k=-p}^{+f}\theta_kX_{t+k}.
\]

\begin{itemize}
\item
  \(p+f+1\) is called the \emph{moving average order}.
\item
  When \(p=f\) the moving average is said to be \emph{centered}. If we
  also have \(\forall k:\:\theta_{-k} = \theta_k\), the moving average
  \(M_{\boldsymbol\theta}\) is said to be \emph{symmetric}. In this
  case, the quantity \(h=p=f\) is called the \emph{bandwidth}.
\end{itemize}

@@

To interpret the notions of gain and phase shift, it is useful to
illustrate the effects of moving averages on harmonic series
\(y_t=\e^{-i\omega t}\) with \(\omega\in[0,\pi]\). The moving average
\(M_{\boldsymbol\theta}\) transforms \(y_t\) into: \[
Y_t = M_{\boldsymbol\theta}y_t = \sum_{k=-p}^{+f} \theta_k \e^{-i \omega (t+k)}
= \left(\sum_{k=-p}^{+f} \theta_k \e^{-i \omega k}\right)\cdot y_t.
\] The function
\(\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{-i \omega k}\)
is called the \emph{transfer function} or \emph{frequency response
function}. The frequency response function can alternatively be defined
as
\(\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{i \omega k}\)
or
\(\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{2\pi i \omega k}\).
It can be rewritten as: \[
\Gamma_{\boldsymbol\theta}(\omega) = \rho_{\boldsymbol\theta}(\omega)\e^{i\varphi_{\boldsymbol\theta}(\omega)},
\] where
\(\rho_{\boldsymbol\theta}(\omega)=G_{\boldsymbol\theta}(\omega)=\lvert\Gamma_{\boldsymbol\theta}(\omega)\rvert\)
is the \emph{gain} or \emph{amplitude} function and
\(\varphi_{\boldsymbol\theta}(\omega)\) is the \emph{phase shift} or
\emph{time shift} function. We this have: \begin{align*}
\rho_{\boldsymbol\theta}(\omega) &=\sqrt{\left(\sum_{k=-p}^{+f}\theta_k\cos(\omega k)\right)^2+
\left(\sum_{k=-p}^{+f}\theta_k\sin(\omega k)\right)^2} \\
\tan \varphi_{\boldsymbol\theta}(\omega) &=- \frac{\sum_{k=-p}^{+f}\theta_k\sin(\omega k)}{\sum_{k=-p}^{+f}\theta_k\cos(\omega k)} \text{ if }\sum_{k=-p}^{+f}\theta_k\cos(\omega k) \ne 0 \\
&= 0 \text{ if }\sum_{k=-p}^{+f}\theta_k\cos(\omega k) = 0.
\end{align*} The phase shift is sometimes represented as
\(\phi_{\boldsymbol\theta}(\omega)=\frac{\varphi_{\boldsymbol\theta}(\omega)}{\omega}\)
to measure it in number of periods. For all symmetric moving averages we
have \(\varphi_{\boldsymbol\theta}(\omega)\equiv 0 \;(modulo\;{\pi})\).

@@

Fourier decomposition allows us to analyze any time series as a sum of
harmonic series, and each component (trend, cycle, seasonal, irregular)
is associated with a set of frequencies. Noting \(\omega = 2\pi/s\), the
harmonic series of frequency \(\omega\) represents a series that repeats
itself every \(s\) periods. For example, for a monthly series (\(s=12\)
observations per year), seasonal movements are those that repeat every
year: they are therefore associated with frequencies \(2\pi/12\) (annual
periodicity), \(2\pi/12\times 2=2\pi/6,\dots,2\pi/12\times 5\). In this
paper, we consider that the trend-cycle is associated with frequencies
in the interval \([0, 2\pi/12]\), i.e.~movements recurring at least
every 12 months. Even if different frequencies are sometimes used
(e.g.~\([0, 2\pi/36]\) to consider only cycles of at least 36 months),
this has no impact on the results of the study. The other frequencies,
\([2\pi/12, \pi]\) are associated with the irregular component.

Figure~\ref{fig-graphsmusgrave} shows the gain and phase shift function
for the asymmetric Musgrave filter (see section~\ref{sec-lppasymf})
often used for real-time trend-cycle estimation (i.e.~when no point in
the future is known). The gain function is greater than 1 on the
frequencies associated with the trend-cycle (\([0, 2\pi/12]\)): this
means that the trend-cycle is well preserved and that short cycles of 1
to 2 years (\([2\pi/24,2\pi/12]\)) are even amplified. At other
frequencies, the gain function is less than 1, but always positive: this
means that the series smoothed by this moving average will always
contain noise, even if it is attenuated. Analysis of the phase shift
shows that the shorter the cycles, the greater the phase shift: this
means that on series smoothed by this moving average, turning points
could be detected at the wrong date.

\begin{figure}

\caption{\label{fig-graphsmusgrave}Coefficients, gain and phase shift
function for the Musgrave filter used in X-11 in real time (last
estimate) for monthly series when the bandwidth is 6.}

@@

Note: the Musgrave filter depends on a ratio \(I/C\) (see
section~\ref{sec-nonparamreg}). In X-11, for monthly series, when the
bandwidth is 6 (i.e.: a symmetric Henderson filter of order 13 is used,
what is used in most cases), the ratio is fixed to 3.5 and this value is
used in this figure.

@@

Trend-cycles are generally modelled by local polynomial trends (see
section~\ref{sec-nonparamreg}) and, in order to best preserve the
trend-cycles, we thus design moving averages that preserve the
polynomial trends. A moving average \(M_{\boldsymbol\theta}\) preserves
a function of time \(f(t)\) if
\(\forall t:M_{\boldsymbol\theta} f(t)=f(t)\).

For the moving average \(M_{\boldsymbol\theta}\), it can be shown that:

\begin{itemize}
\tightlist
\item
  \(M_{\boldsymbol\theta}\) preserves polynomials of degree \(d\) if and
  only if: \[
  \sum_{k=-p}^{+f}\theta_k=1
   \text{ and }
  \forall j \in \left\{1,2,\dots,d\right\}:\:
  \sum_{k=-p}^{+f}k^j\theta_k=0.
  \]
\item
  If \(M_{\boldsymbol\theta}\) is symmetric (\(p=f\) and
  \(\theta_{-k} = \theta_k\)) and preserves polynomials of degree \(2d\)
  then it also preserves polynomials of degree \(2d+1\).
\end{itemize}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Use asymmetric moving averages to take account of the lack of
  available data;
\item
  Apply symmetric filters to extended forecast series. This method seems
  to date back to \textcite{deforest1877adjustment}, which also suggests
  modelling a polynomial trend of degree three or less at the end of the
  period. A similar approach is used in the X-13ARIMA-SEATS seasonal
  adjustment method: the series is extend by one year (by default) with
  an ARIMA model to minimise the revisions associated to asymmetric
  filters. Since the final filter used for the seasonal adjustment
  extraction is much longer than one year (in most of the cases, for
  monthly series, the bandwidth is 78), the input series is just
  partially extended (and asymmetric filters are still used) to prevent
  from instability over long periods (e.g., outliers or model shifts).
\end{enumerate}

Ultimately, the second method is equivalent to using asymmetric moving
averages, since forecasts are linear combinations of the past.

>>>>

\usepackage{stmaryrd}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{ragged2e}
\usepackage{animate, dsfont, here, xspace}
%\usepackage{tikz}
\usepackage{tikz,pgfplots}
 \pgfplotsset{compat=1.17}
%\includepdf[fitpaper=true, pages=-]{img/pdg.pdf}

@@

%\DefineBibliographyStrings{english}{andothers={et\addabbrvspace alii}}
\usepackage[authordate16,backend=biber,maxcitenames=2]{biblatex-chicago}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{british}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{biblatex}
\addbibresource{biblio.bib}
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Improving real-time trend estimates using local parametrisation of polynomial regression filters},
  pdflang={en-GB},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

This paper examines and compares real-time estimates of the trend-cycle
component using moving averages constructed with local polynomial
regression. It enables to reproduce Henderson's symmetric and Musgrave's
asymmetric filters used in the X-13ARIMA-SEATS seasonal adjustment
algorithm. This paper proposes two extensions of local polynomial
filters for real-time trend-cycle estimates: first including a
timeliness criterion to minimise the phase shift; second with procedure
for parametrising asymmetric filters locally while they are generally
parametrised globally, which can be suboptimal around turning points. An
empirical comparison, based on simulated and real data, shows that
modelling polynomial trends that are too complex introduces more
revisions without reducing the phase shift, and that local
parametrisation reduces the delay in detecting turning points and
reduces revisions. The results are reproducible and all the methods can
be easily applied using the R package \texttt{rjd3filters}.

@@

Analysis of the economic cycle, and in particular the early detection of
turning points, is a major topic in the analysis of economic outlook. To
achieve this, economic indicators are generally seasonally adjusted.
However, in order to improve their interpretability, it may be necessary
to perform additional smoothing to reduce noise, thereby to analyse the
trend-cycle component. By construction, trend-cycle extraction methods
are closely related to seasonal adjustment methods, since they are
generally applied to seasonally adjusted series.

A moving average, or linear filter, is a statistical method that
consists of applying a rolling weighted mean to a times series: for each
date \(t\) it computes a weighted mean of \(p\) past points and \(q\)
future points where \(p,q\geq0\) depends on the moving average. They are
ubiquitous in business cycle extraction and seasonal adjustment methods.
For example, the X-11 seasonal adjustment method
\autocite{ladiray2011seasonal}, used in X-13ARIMA-SEATS software
\autocite{x13}, uses several moving averages to estimate the main
components of a time series. Symmetric filters are applied to the centre
of the series and for trend-cycle extraction, the most popular symmetric
filter is the \textcite{henderson1916note} moving average, which is used
in the X-11 seasonal adjustment algorithm. However, for real-time
estimates, due to the lack of future observations, all these methods
must rely on asymmetric filters to estimate the most recent points. For
example, for trend-cycle extraction, X-11 uses Henderson's symmetric
filter and \textcite{musgrave1964set}'s asymmetric filters on an
extended series using an ARIMA model. Since the predicted values are
linear combinations of past values, this amounts to applying asymmetric
moving averages at the end of the series. If the classic asymmetric
moving averages have good properties regarding the future revisions
induced by the process (for example \textcite{pierce1980SA} shows
similar performances in terms of revisions of X-11 compared to
theoretically superior procedure based on ARIMA forecast models), they
create, by construction, phase shifts that impact the real-time
estimation of turning points, introducing time delay in the detection.

Using local polynomial regression, \textcite{proietti2008} developed a
general class of symmetric and asymmetric moving averages. In
particular, this class encompass Henderson's symmetric filter and
Musgrave's asymmetric filters. The aim of this study is to propose two
extensions to the \textcite{proietti2008} class of filters in order to
take account of two drawbacks of those methods. Firstly adding, in the
optimisation process, a timeliness criterion to directly control the
phase shift (i.e., the delay in detecting turning points). Secondly
calibrating asymmetric filters locally, while they are generally
calibrated globally using thus assumptions that may be wrong locally.
Those extensions are implemented in the statistical software R
\autocite{logicielr} throw the \texttt{rjd3filters} package
\autocite{rjd3filters} and can therefore be easily used. All the code
associated to this paper is available at \url{https://github.com/XXXX}
(anonymized linked before the manuscript is accepted).

@@

The basic assumption used in time series decomposition methods is that
the input observed time series, \(y_t\), can be decomposed into a signal
component \(\mu_t\) and an erratic component \(\varepsilon_t\) (called
irregular): \[
f(y_t)=\mu_t+\varepsilon_t
\] where \(f\) denotes some appropriate transformation (usually
logarithmic or no transformation). To simplify further notations,
\(y_t\) will denote the transformed observed series. The noise component
\(\varepsilon_t\) is usually assumed to be a white noise. Assuming that
the input time series is seasonally adjusted (or without seasonality),
the signal \(\mu_t\) represents the trend (sustained and systematic
variations over a long period of time) and cycle (cyclical movements
superimposed upon the long-term trend) components, here estimated
jointly and called trend-cycle \(TC_t\). This component can be locally
approximated by a polynomial degree (section~\ref{sec-nonparamreg}): \[
\mu_t = \sum_{j=0}^d\beta_jt^j+\xi_t
\] with \(\xi_t\) a stochastic process uncorrelated with
\(\varepsilon_t\). Even if some papers model \(\xi_t\) and
\(\varepsilon_t\) separately \autocite[see for
example][]{GrayThomson2002}, a usual assumption, adopted in this paper,
is to is to gather \(\xi_t\) and \(\varepsilon_t\). Thus, the
trend-cycle \(TC_t\) is considered as deterministic and modelled as a
polynomial trend of degree \(d\). The coefficients
\((\beta_0,\dots,\beta_k)\) can be estimated by weighted least squares.
The estimate \(\hat \beta_0\) provides the trend-cycle estimate
\(\widehat{TC}_t\) and it can be shown that this equivalent to apply of
moving average (section~\ref{sec-nonparamreg}). The goal of this paper
is to present two new methods to separate the trend-cycle component from
the noise component in real-time (i.e., when no future point is known),
using moving averages build on local polynomial smoothing techniques.

@@

Let \(p\) and \(f\) two integers, a moving average
\(M_{\boldsymbol\theta}\) is defined by a set of coefficients
\(\boldsymbol\theta=\transp{\begin{pmatrix}\theta_{-p}&\cdots&\theta_{f}\end{pmatrix}}\)
such as for all time series \(y_t\): \[
M_{\boldsymbol\theta}(y_t)=\sum_{k=-p}^{+f}\theta_kX_{t+k}.
\]

\begin{itemize}
\item
  \(p+f+1\) is called the \emph{moving average order}.
\item
  When \(p=f\) the moving average is said to be \emph{centred}. If we
  also have \(\forall k:\:\theta_{-k} = \theta_k\), the moving average
  \(M_{\boldsymbol\theta}\) is said to be \emph{symmetric}. In this
  case, the quantity \(h=p=f\) is called the \emph{bandwidth}.
\end{itemize}

@@

To interpret the notions of gain and phase shift, it is useful to
illustrate the effects of moving averages on harmonic series
\(y_t=\e^{-i\omega t}\) with \(\omega\in[0,\pi]\). The moving average
\(M_{\boldsymbol\theta}\) transforms \(y_t\) into: \[
Y_t = M_{\boldsymbol\theta}y_t = \sum_{k=-p}^{+f} \theta_k \e^{-i \omega (t+k)}
= \left(\sum_{k=-p}^{+f} \theta_k \e^{-i \omega k}\right)\cdot y_t.
\] The function
\(\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{-i \omega k}\)
is called the \emph{transfer function} or \emph{frequency response
function}. The frequency response function can alternatively be defined
as
\(\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{i \omega k}\)
or
\(\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{2\pi i \omega k}\).
It can be rewritten as: \[
\Gamma_{\boldsymbol\theta}(\omega) = \rho_{\boldsymbol\theta}(\omega)\e^{i\varphi_{\boldsymbol\theta}(\omega)},
\] where
\(\rho_{\boldsymbol\theta}(\omega)=G_{\boldsymbol\theta}(\omega)=\lvert\Gamma_{\boldsymbol\theta}(\omega)\rvert\)
is the \emph{gain} or \emph{amplitude} function and
\(\varphi_{\boldsymbol\theta}(\omega)\) is the \emph{phase shift} or
\emph{time shift} function. We thus have: \begin{align*}
\rho_{\boldsymbol\theta}(\omega) &=\sqrt{\left(\sum_{k=-p}^{+f}\theta_k\cos(\omega k)\right)^2+
\left(\sum_{k=-p}^{+f}\theta_k\sin(\omega k)\right)^2} \\
\tan \varphi_{\boldsymbol\theta}(\omega) &=- \frac{\sum_{k=-p}^{+f}\theta_k\sin(\omega k)}{\sum_{k=-p}^{+f}\theta_k\cos(\omega k)} \text{ if }\sum_{k=-p}^{+f}\theta_k\cos(\omega k) \ne 0 \\
&= 0 \text{ if }\sum_{k=-p}^{+f}\theta_k\cos(\omega k) = 0.
\end{align*} The phase shift is sometimes represented as
\(\phi_{\boldsymbol\theta}(\omega)=\frac{\varphi_{\boldsymbol\theta}(\omega)}{\omega}\)
to measure it in number of periods. For all symmetric moving averages we
have \(\varphi_{\boldsymbol\theta}(\omega)\equiv 0 \;(modulo\;{\pi})\).

@@

Fourier decomposition allows us to analyse any time series as a sum of
harmonic series, and each component (trend, cycle, seasonal, irregular)
is associated with a set of frequencies. With \(\omega = 2\pi/s\), the
harmonic series of frequency \(\omega\) represents a series that repeats
itself every \(s\) periods. For example, for a monthly series (\(s=12\)
observations per year), seasonal movements are those that repeat every
year: they are therefore associated with frequencies \(2\pi/12\) (annual
periodicity), \(2\pi/12\times 2=2\pi/6,\dots,2\pi/12\times 5\). In this
paper, we consider that the trend-cycle is associated with frequencies
in the interval \([0, 2\pi/12]\), i.e., movements recurring at least
every 12 months. Even if different frequencies are sometimes used
(e.g.~\([0, 2\pi/36]\) to consider only cycles of at least 36 months),
this has no impact on the results of the study. The other frequencies,
\([2\pi/12, \pi]\) are associated with the irregular component.

Figure~\ref{fig-graphsmusgrave} shows the gain and phase shift function
for the asymmetric Musgrave filter (see section~\ref{sec-lppasymf})
often used for real-time trend-cycle estimation (i.e., when no point in
the future is known). The gain function is greater than 1 on the
frequencies associated with the trend-cycle (\([0, 2\pi/12]\)): this
means that the trend-cycle is well preserved and that short cycles of 1
to 2 years (\([2\pi/24,2\pi/12]\)) are even amplified. At other
frequencies, the gain function is less than 1, but always positive: this
means that the series smoothed by this moving average will always
contain noise, even if it is attenuated. Analysis of the phase shift
shows that the shorter the cycles, the greater the phase shift: this
means that on series smoothed by this moving average, turning points
could be detected at the wrong date.

\caption{\label{fig-graphsmusgrave}Coefficients, gain and phase shift
function for the Musgrave filter used in X-11 in real-time (last
estimate) for monthly series when the bandwidth is 6.}

@@

\justifying

\emph{Lecture: on monthly times series, 12-month cycles (associated to
the frequency \(2\pi/12=\pi/6\)) are amplified by 10\%
(\(G_{\boldsymbol\theta}(\pi/6)\simeq1.1\)) and associated turning
points are detected with a delay of 1 months
(\(\varphi_{\boldsymbol\theta}(\pi/6)/(\pi/6)\simeq -1\)).}
\emph{8-month cycles (associated to the irregular) are only reduced by
6\% (\(G_{\boldsymbol\theta}(\pi/4)\simeq0.94\)).}\\
\emph{Note: the Musgrave filter depends on a ratio denoted \(I/C\) (see
section~\ref{sec-nonparamreg}).} \emph{In X-11, for monthly series, when
the bandwidth is 6 (i.e.: a symmetric Henderson filter of order 13 is
used, what is used in most cases), the ratio is fixed to 3.5 and this
value is used in this figure.}

@@

Trend-cycles are generally modelled by local polynomial trends (see
section~\ref{sec-nonparamreg}) and, in order to best preserve the
trend-cycles, we thus design moving averages that preserve the
polynomial trends. A moving average \(M_{\boldsymbol\theta}\) preserves
a function of time \(f(t)\) if
\(\forall t,M_{\boldsymbol\theta} f(t)=f(t)\).

For a moving average \(M_{\boldsymbol\theta}\), it can be shown that:

\begin{itemize}
\tightlist
\item
  \(M_{\boldsymbol\theta}\) preserves polynomials of degree \(d\) if and
  only if: \[
  \sum_{k=-p}^{+f}\theta_k=1
   \text{(preserves constant) and }
  \forall j \in \left\{1,2,\dots,d\right\},\:
  \sum_{k=-p}^{+f}k^j\theta_k=0.
  \]
\item
  If \(M_{\boldsymbol\theta}\) is symmetric (\(p=f\) and
  \(\theta_{-k} = \theta_k\)) and preserves polynomials of degree \(2d\)
  then it also preserves polynomials of degree \(2d+1\).
\end{itemize}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Use asymmetric moving averages to take account of the lack of
  available data;
\item
  Apply symmetric filters to an extended forecast series (which is
  equivalent to using asymmetric moving averages, since forecasts are
  linear combinations of the past). This method seems to date back to
  \textcite{deforest1877adjustment}, which also suggests modelling a
  polynomial trend of degree three or less at the end of the period. A
  similar approach is used in the X-13ARIMA-SEATS seasonal adjustment
  method: the series is extended by one year (by default) with an ARIMA
  model to minimise the revisions associated to asymmetric filters.
  Since the final filter used for the seasonal adjustment extraction is
  much longer than one year (in most of the cases, for monthly series,
  the bandwidth is 78), the input series is just partially extended (and
  asymmetric filters are still used) to prevent from instability over
  long periods (e.g., outliers or model shifts).
\end{enumerate}

### 2024-04-30 paper/resp_referee.qmd
v1

---
title: "Response to referee"
format: pdf
---

@@

*It was added in the beginning of new sections 3 and 4 than the bandwidth is fixed.* 
*Nearest neighbour bandwidth was added in supplemental material but it doesn't improve the results in therm of phase shift.* 
*One explanation could be that the bias is higher with LC/QL methodes (we model linear trend using higher bandwidth) and for other methods (e.g. DAF) that the revisions to the final symmetric filters are higher.*

@@

*The term "undersirable oscillations" was removed*

@@

> The author simulates time series of length 60 years to illustrate the methodology at the end of the series.
It may be worth considering (in addition) shorter series. 
Another thought is that the ARIMA model being used to extend the series appears to be modeled using the full series; what if the ARIMA model used to extend the series was instead estimated using just a short span toward the end of the series?

@@

*Figures are now black and white a scaled gray legend.*
*In some of them, there are indeed a lot of information with several labels, but the goal is not to be able to read all the details of all the lines but to see the general behavior of the filters (for example if the implicit forecasts seem relevant or not)*

@@

*We try to clarify in the section associated to the proposed methods: all the functions mentionned are already in rjd3filters.*
*The local parametrisation is not directly in the package but can be easily implemented (especially because the code is available): the variance estimator is in the package but not the moving-averages associated to slope/concavity estimators (which can be easily derived)*

@@

*TODO*

@@

*A lecture note is added in the tables and more explainations are added to the text*

@@

*We try to clarify the contribution in the abtract, introduction and in the beginning of sections 2 and 3*

>>>>

---
title: "Response to referee"
# format: docx
format: pdf
lang: en-GB  
---

We would like to thanks all the reviewers and the associate editor for the comments, suggestions and the time spent proofreading the paper.

@@

*It was added in the beginning of new sections 3 and 4 than the bandwidth is fixed.* 
*Nearest neighbour bandwidth was added in supplemental material but it doesn't improve the results in therm of phase shift.* 
*One explanation could be that the bias is higher with LC/QL methods (we model linear trend using higher bandwidth) and for other methods (e.g. DAF) that the revisions to the final symmetric filters are higher.*

@@

*The term "undesirable oscillations" was removed*

@@

> The author simulates time series of length 60 years to illustrate the methodology at the end of the series.
It may be worth considering (in addition) shorter series. 
Another thought is that the ARIMA model being used to extend the series appears to be modelled using the full series; what if the ARIMA model used to extend the series was instead estimated using just a short span toward the end of the series?

@@

*Figures are now black and white a scaled gray legend.*
*In some of them, there are indeed a lot of information with several labels, but the goal is not to be able to read all the details of all the lines but to see the general behaviour of the filters (for example if the implicit forecasts seem relevant or not)*

@@

*We try to clarify in the section associated to the proposed methods: all the functions mentioned are already in rjd3filters.*
*The local parametrisation is not directly in the package but can be easily implemented (especially because the code is available): the variance estimator is in the package but not the moving-averages associated to slope/concavity estimators (which can be easily derived)*

@@

*More explanation with the reference in parentheses*

@@

*A lecture note is added in the tables and more explanations are added to the text*

@@

*We try to clarify the contribution in the abstract, introduction and in the beginning of sections 2 and 3*
